---
title: "p8105_hw1_zh2493"
output: github_document
---

## Problem 1

```{r}
library(tidyverse)

df = tibble(
  vec_numeric = rnorm(10, mean = 0, sd = 1),
  vec_logical = vec_numeric > 0,
  vec_char = c("M", "Y", "N", "A", "M", "E", "I", "S", "Z", "Q"),
  vec_factor = factor(c("blue", "blue", "yellow", "yellow", "yellow", "yellow", "green", "green", "green", "green"))
)
df
```

```{r}
mean1_df = mean(pull(df, vec_numeric))
mean1_df

mean2_df = mean(pull(df, vec_logical))
mean2_df

mean3_df = mean(pull(df, vec_char))
mean3_df

mean4_df = mean(pull(df, vec_factor))
mean4_df

```
There are two warning messages because column 3 and column 4 is not numeric or logical, so they do not have mean.


```{r eval = FALSE}

vec_logical = as.numeric(vec_logical)
vec_char = as.numeric(vec_char)
vec_factor = as.numeric(vec_factor)
```
when i run it, i find that the logical vector and the factor vector can turn to numeric. However, the character vector can not turn to numeric.


##Problem 2

```{r}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```
The names of the data are `r names(penguins)`.

The number of the row in the data is `r nrow(penguins)` and the number of the column in the data is `r ncol(penguins)`.

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

```{r}

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) +
  geom_point(aes(color = species))
ggsave("scatterplot.pdf")
```

























